Treefelling_Sylvain's version

### 2021-07-30 R/Treefelling_Sylvain's version.Rmd

# Application in a dataframe
FellingTrees <- SelectedTrees %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# Marche pas encore
FellingTrees <- inventory %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              st_tree(.,
                      ScndTrail = ScndTrail,
                      MainTrail = MainTrail,
                      fuel = "2", directionalfelling ="2",
                      advancedloggingparameters = loggingparameters())$A,
              NULL)) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

@@

ggplot() +
  # geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  # geom_sf(data = TrailPt) +
  geom_sf(data = FellingTrees)
```

```{r}
st_tree(SelectedTrees[1,],
        ScndTrail = ScndTrail,
        MainTrail = MainTrail,
        fuel = "2", directionalfelling ="2",
        advancedloggingparameters = loggingparameters())$A

@@

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% 
  do(treepolygon = 
       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A %>% 
       st_as_text()) %>% 
  unnest(treepolygon)

@@

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = get_treepolygon(inventory2), fill = "red")

>>>>

# Application in a dataframe
FellingTrees <- SelectedTrees %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table

@@

ggplot() +
  # geom_sf(data = Foot) +
  # geom_sf(data = TrailPt) +
  geom_sf(data = FellingTrees)
```

```{r}

st_tree(SelectedTrees[1,],
        ScndTrail = ScndTrail,
        MainTrail = MainTrail,
        fuel = "2", directionalfelling ="2",
        advancedloggingparameters = loggingparameters())$A

@@

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>%

       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A %>% 
       st_as_text())  # as text to easy join with a non spacial table
  # unnest(treepolygon) # display the small dataframe in the big dataframe in one

inventory <- left_join(inventory, felttrees) # join spatial filtered inventory and non spatial complete inventory

get_treepolygon <- function(inventory){ # function from text (wkt) to sf
       st_as_text()) %>% 
  unnest(treepolygon)

@@

ggplot() +
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) + # all the individuals of the plot
  geom_sf(data = get_treepolygon(inventory), fill = "red") # trees polygons

st_intersection( # trees under the fallen trees
  get_treepolygon(inventory),
  geom_sf(data = st_as_sf(inventory, coords = c("Xutm", "Yutm"))) +
  geom_sf(data = get_treepolygon(inventory2), fill = "red")
